---
title: "Working with MediDateR"
author: "Christopher Hughes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

MediDateR is a package for working with medical-style data. The workhorse function is \code{data_roll_up}. This rolls up contiguous data time windows based on a set \code{start_end_log}.

## Functions

### \code{read_data}

Reads in rds or csv data

\code{filepath} the filepath to the raw data
\code{filetype} a character for the file extension ("csv" or "RDS")

Tibble of data or an error for invalid file extensions

### \code{data_roll_up}

Rolls up contiguous data time windows based on a set \code{start_end_log}

\code{data} a dataframe with attributes:id, dtstart, dtend
\code{start_end_lag} defined lag between the end time and the following start time in days. Set to 1 (day) as default.

Data is returned in a tibble

## Example

You can take a table of data and roll it up.

```{r}
library(dplyr)
library(mediDateR)

data_t <- tibble(
   id = c(1,1,1,1,2,2,3,3),
   dtstart = c(1,8,14,16,17,22,29,33 ),
   dtend = c(8,14,16,17,19,24,33,35)
)
knitr::kable(data_t)
```

As there are overlapping values the start_end_lag set to 0 gives 4 separate time windows from the tibble data_t

```{r}

data_roll_default <- data_roll_up(data_t, start_end_lag = 0)
knitr::kable(data_roll_default)

```

Without a default, \code{data_roll_up} will return the same data as the default lag is set to 1 and there is no lag between any of the start and end times.

```{r}

# start_end_lag is not set so the default value, 1, is used.
data_roll_default <- data_roll_up(data_t)
knitr::kable(data_roll_default)

```


For updates and infomation go to:

([MediDateR on GitHub](https://github.com/ch4413/medidater))
